Fluent statistical computing interfaces for biological data analysis

### 2020-08-03 Rmd/00-d-acknowlegements.Rmd
typos and additional thanks

I would like to thank my colleagues Charity Law, Peter Hickey, and Saskia Freytag for their friendship and guidance on all things statistical during my thesis. I look forward to having a drink with you in person.

>>>>

I would like to thank my colleagues Charity Law, Peter Hickey, Alexandra Garnham, Hannah Coughlan, and Saskia Freytag for their friendship and guidance on all things statistical during my thesis. I look forward to having a drink with you in person.
